% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Scott Clark} & \textbf{\today} \\
\texttt{scott@scottclark.io} & \texttt{www.scottclark.io} \\
\texttt{@DrScottClark} & \texttt{github.com/sc932 \& github.com/Yelp/MOE}

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Cornell University}{Ithaca, NY}{Ph.D. Applied Mathematics, M.S. Computer Science}{2008 - 2012}
	\begin{itemize}
		\resitem{Department of Energy Computational Science Graduate Fellow (Full Scholarship, 4 years)}
		\resitem{Machine Learning, Data Science, Data Mining in bioinformatics and global optimization}
	\end{itemize}

\item
	\ressubheading{Oregon State University}{Corvallis, OR}{B.Sc. Mathematics, B.Sc. Computational Physics, B.Sc. Physics}{2004 - 2008}
	\begin{itemize}
		\resitem{Graduated Magna Cum Laude with minors in Actuarial Sciences and Mathematical Sciences}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Development:} Python (preferred), C/C++, CUDA, JavaScript, \LaTeX

\item {\bf Numerical Analysis and Computer Science:} Machine Learning, Data Mining, Optimization, Computational Science, Artificial Intelligence, Linear Algebra, Monte Carlo Methods, ODEs, PDEs, Iterative Methods, Parallel Programming, Distributed Systems, Data Structures

\item {\bf Technology:} MapReduce, numerical libraries, web frameworks, databases, linux, git, vim, tmux

\item Exploring and implementing ideas. Give me an API/dataset and a problem and I will figure it out.

\item Diverse background in Software Engineering, Math, Computer Science, Physics and Biology allows me to communicate within a wide technical scope and start contributing to any group immediately.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research and Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Yelp Inc}{San Francisco, CA}{Data Mining Engineer and Lead on Ad Targeting Team}{July 2012 - current}
	\begin{itemize}
            \resitem{{\bf Optimization:} Co-developed and led team for MOE: the Metric Optimization Engine (\texttt{github.com/Yelp/MOE}, an \textbf{open source} optimization framework), found significant gains in different metrics across the organization using Bayesian Global Optimization algorithms.}
            \resitem{{\bf Targeting:} Implemented multi-armed bandit strategies for ad selection, sole targeting engineer on mobile app ads rollout, developed new location-based targeting algorithms, advised and helped develop other machine learning and math based targeting projects.}
            \resitem{{\bf Leadership:} Led cross-organization teams as director of the Yelp Dataset Challenge, MOE team lead, intern and new-hire mentor, founder and organizer of Applied Learning Group (bi-weekly, all-engineering technical speaker series) and more. Successfully managed projects from inception to on-time completion; balancing tradeoffs and coordinating teamwork.}
            \resitem{{\bf Recruiting:} Created, implemented, and directed \texttt{yelp.com/dataset\_challenge}, gave many dozens of tech talks across the country, led events, gave hundreds of technical interviews, and closed candidates.}
	\end{itemize}

\item
	\ressubheading{Bloomberg LP}{New York, NY}{Financial Software Development Intern}{Summer 2011}
	\begin{itemize}
		\resitem{Developed end-to-end reporting software in \texttt{C++} and \texttt{javascript}}
    \resitem{Implemented statistical models to perform forward and backward portfolio analysis}
	\end{itemize}

\item
	\ressubheading{DOE Joint Genome Institute (Lawrence Berkeley National Lab)}{Walnut Creek, CA}{Researcher in Analysis Group under Dr. Zhong Wang}{Summer 2010}
	\begin{itemize}
		\resitem{Created \textbf{open source} genome validation software tool in \texttt{python} and \texttt{C} (alescore.org)}
    \resitem{Used machine learning to mine TBs of genome data efficiently using novel likelihood function}
	\end{itemize}

\item 
	\ressubheading{Los Alamos National Laboratory}{Los Alamos, NM}{Researcher in Metagenomics Group under Dr. Nick Hengartner}{Summer 2009}
	\begin{itemize}
		\resitem{Wrote \textbf{open source} alignment algorithm software tool in \texttt{python}, \texttt{C} and \texttt{CUDA}}
    \resitem{Used statistical models to discover sequence alignments using parallel algorithms on GPUs}
	\end{itemize}

\item
	\ressubheading{Oregon State University}{Corvallis, OR}{Research Assistant under Prof. Malgorzata Peszynska and Prof. Rubin Landau}{2005-2008}
	\begin{itemize}
		\resitem{Finite element analysis with uncertainty and web-based teaching in \texttt{Java}}
	\end{itemize}

\item
	\ressubheading{Max Plank Institute for the Physics of Complex Systems}{Dresden, Germany}{NSF REU Research Assistant under Prof. Steven Tomsovic}{Summer 2007}
	\begin{itemize}
		\resitem{Research on extreme value statistics in \texttt{MATLAB} and \texttt{FORTRAN}}
	\end{itemize}

\item
	\ressubheading{University of California: Davis}{Davis, CA}{NSF REU Research Assistant under Prof. Daniel Cox}{Summer 2006}
	\begin{itemize}
		\resitem{Computational biophysics research as applied to protein folding in \texttt{Java}}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Selected Open Source Projects}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
    \ressubheading{MOE: Metric Optimization Engine (\texttt{github.com/Yelp/MOE})}{Python, C++, CUDA}{A global, black box optimization engine for real world metric optimization}{2010 - Current}
    \begin{itemize}
        \resitem{Implemented throughout Yelp, optimizing ad metrics. 2nd most popular open source project.}
        \resitem{Talk: \texttt{bit.ly/1plYZA2}, Slides: \texttt{slidesha.re/1zOrOJy}, Blog: \texttt{bit.ly/1x73xdr}}
        \resitem{Presented to executives, universities, conferences and companies around the country.}
	\end{itemize}

\item
    \ressubheading{My Resume/CV (\texttt{github.com/sc932/resume})}{\LaTeX}{This resume and my CV.}{2010 - current}
    \begin{itemize}
        \resitem{280+ GitHub stars, previous \#1 article on Hacker News, 60+ forks.}
	\end{itemize}

\item
    \ressubheading{ALE: Assembly Likelihood Estimator (\texttt{github.com/sc932/ALE})}{C, Python}{Probabilistic evaluation of genome assemblies}{2010 - 2013}
    \begin{itemize}
        \resitem{Uses statistical function to score and rank genome assemblies, published in Bioinformatics}
	\end{itemize}

\end{itemize}

\resheading{Writing and Awards}

\begin{itemize}

\item {\bf Department of Energy Computational Science Graduate Fellow:} Four year full fellowship. $\sim$20 awarded nationally per year. Won the Communicating Science award (\texttt{bit.ly/VbcTZK}).
\item {\bf Yelp Blog:} Wrote several posts announcing the open sourcing of MOE, the Yelp Dataset Challenge and more. \texttt{bit.ly/1x73xdr}, \texttt{bit.ly/1oCCZvv}, \texttt{bit.ly/1sOsEBS}, \texttt{bit.ly/1plX7Hk}
\item {\bf Press:} WSJ: \texttt{on.wsj.com/VaOvqQ}, Cornell: \texttt{bit.ly/1oB2dzm},  DIEXIS: \texttt{bit.ly/1oofbl4}

\end{itemize}

\end{document}
